### 2019-06-27 inst/vign/taxize_vignette.Rmd
fix urls in vignette to https - skip progressor tests on cran

[eol]: http://www.eol.org/
[ncbi]: http://www.ncbi.nlm.nih.gov/
[itis]: http://www.itis.gov/
[wikispecies]: http://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/

>>>>

[eol]: https://www.eol.org/
[ncbi]: https://www.ncbi.nlm.nih.gov/
[itis]: https://www.itis.gov/
[wikispecies]: https://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/
